Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-03-17 article-models-tt.tex
small improvement

In our treatment, a context can be the empty context or it can be a binary
planar tree of which `the leaves are (families of) contexts'. 
The judgmental equality relation on contexts is an equivalence relation which 
expresses that binary planar
trees of contexts are judgmentally equal if their leaves are, taking only the
order of the leaves into account \emph{and not the actual shape of the three}.
The intuition behind this equivalence relation is indeed that unstructured
(i.e.~unbracketed) lists such as the lists of variable declarations which
usually appear in type theoretical syntax, may be regarded as contexts.

>>>>

In our treatment, a context can be the empty context or it can be a binary
planar tree of which `the leaves are (families of) contexts'. 
The judgmental equality relation on contexts is an equivalence relation which 
expresses that binary planar
trees of contexts are judgmentally equal if their leaves are, taking only
(the isomorphism class of) 
the order of the leaves into account \emph{and not the actual shape of the three}.
The intuition behind this equivalence relation is indeed that unstructured
(i.e.~unbracketed) lists such as the lists of variable declarations which
usually appear in type theoretical syntax, may be regarded as contexts.
